---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fars

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/mentoldo/fars.svg?branch=main)](https://travis-ci.com/mentoldo/fars)
<!-- badges: end -->

The goal of fars is to describe data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, in the time period 2013-2015.
It has two functions `fars_summarize_years` and `fars_map_state`

## Installation

You can install the development version of fars like so:

``` r
install_github('mentoldo/fars', build_vignettes=TRUE)
```

## Example

It has two functions `fars_summarize_years` and `fars_map_state`.  

`fars_summarize_years` makes a frecuency table for accidents by months for years passed as arguments for all US States.

```{r example_summarize_years, warning=FALSE, message=FALSE}
library(fars)
## basic example code
library(kableExtra)

fars_summarize_years(c(2013, 2014, 2015)) %>% 
  kable()

```

`fars_map_state` plots the geolalization of all fatal crashes in highways in the indicated year and state.

```{r example_map_state}
fars_map_state(26, 2015)
```
