---
title: "Quickstart"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quickstart}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fars)
```

## Aims of the package

This package is part of an assignment for Building R Packages of Coursera. This package allows you to describe data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, in the time period 2013-2015.
It has two functions `fars_summarize_years` and `fars_map_state`.  

`fars_summarize_years` makes a frecuency table for accidents by months for years passed as arguments for all US States.

```{r fars_summarize_years, message=FALSE, warning=FALSE}
fars_summarize_years(c(2013, 2014, 2015))
```

`fars_map_state` plots the geolalization of all fatal crashes in highways in the indicated year and state.

```{r fars_map_state}
fars_map_state(26, 2015)
```

